\beginTestedClass{ProjectExplorerPanel}

\beginCase{Directory text field}
\condition{Shows autocomplete popup when typing and typed text matches to one or more directory}
\testDescription{Typed different letters, worked fine. Funny results with '.' and it searched subdirectories with '..'}\testResultTrue
\condition{Shows directory history on down-arrow click}
\testDescription{Works fine, only down-arrow fires this when no autocomplete pop-up is active}\testResultTrue
\condition{Too long lines in popup are shortened}
\testDescription{Tried both pop-ups}\testResultTrue
\condition{Tries to change directory when on enter press or mouse-click to popupmenu (UC21)}
\testDescription{Mouse click on autocomplete pop-up didnt work, history ok}\testResultFailed
\condition{Only allows correct and existing directories (flashes red on change-attempt if invalid)}
\testDescription{Tried existing and non-existing directories, ok. But with '.' and '..' it tries to open those. Strange.}\testResultTrue
\closeCase

\beginCase{Browse-button}
\condition{Opens a dir chooser dialog}
\testDescription{Tried with different values on Directory text field. Opened last good directory in dialog.}\testResultTrue
\condition{Changes to chosen directory if "Open" selected; updates text field (UC21)}
\testDescription{Opens only if directory exists}\testResultTrue
\closeCase

\beginCase{Project file table}
\condition{Shows project files in current directory}
\testDescription{Updates on the fly while changing directories}\testResultTrue
\condition{Only shows project files (.ika and Calibration/AF/Thellier/Thermal)}
\testDescription{Tried various directories}\testResultTrue
\condition{Hilights open project}
\testDescription{Changed project with mouse and keyboard}\testResultTrue
\condition{Hilights (with different color) currently measuring project}
\testDescription{Colors work fine combined with open-measure, multiple selections.}\testResultTrue
\condition{Loads project on project file mouseclick (UC20)}
\testDescription{Opens on left-mouse click only}\testResultTrue
\condition{Show export menu for clicked file on right-click}
\testDescription{Works both single and multiple selections and dont open if no selections}\testResultTrue
\condition{Export to selected file if any chosen (UC13-UC15)}
\testDescription{Single and multiple exports fine, only dat is supported?}\testResultTrue
\condition{Sorts data on header click}
\testDescription{Tested all three choices in all combinations}\testResultTrue
\condition{Updates data if changed (modifield-column, that is)}
\testDescription{Tested changing between two directories}\testResultTrue
\closeCase

\beginCase{"Create New" -components}
\condition{Only allows correct, non-existing files; flashes red if invalid}
\testDescription{$\backslash$ don't work. Checks name for all differend projects, cannot have same named project in AF and Thellier for example}\testResultFalse
\condition{If valid filename, creates it, updates table with created file selected (UC19)}
\testDescription{Tested with various new Projects, AF, Thellier and Thermal}\testResultTrue
\closeCase

\closeTestedClass
