\beginClass{ProjectInformationPanel}
\classPackage{ikayaki.gui}
\classDeclaration{public class ProjectInformationPanel}
\classExtends{ProjectComponent}
\classCreatedBy{MainViewPanel}
\classComment{Allows inserting and editing project information.}
\classEvent{On change of contest in textfield}{Notify project about
change in project information.}
\classEvent{On project event}{Update textfields to correspond new
project information.}
\closeClass

\beginField{operatorLabel}
\fieldDeclaration{private JLabel operatorLabel}
\closeField

\beginField{operatorTextField}
\fieldDeclaration{private JTextFiels operatorTextField}
\closeField

\beginField{dateLabel}
\fieldDeclaration{private JLabel dateLabel}
\closeField

\beginField{dateTextField}
\fieldDeclaration{private JTextFiels dateTextField}
\closeField

\beginField{measurementType}
\fieldDeclaration{private ButtonGroup measurementType}
\fieldComment{Groups autoMeasurement and manualMeasurement radiobuttons.}
\closeField

\beginField{autoMeasurement}
\fieldDeclaration{private JRadioButton autoMeasurement}
\closeField

\beginField{manualMeasurement}
\fieldDeclaration{private JRadioButton manualMeasurement}
\closeField

\beginField{rocktypeLabel}
\fieldDeclaration{private JLabel rocktypeLabel}
\closeField

\beginField{rocktypeTextField}
\fieldDeclaration{private JTextFiels rocktypeTextField}
\closeField

\beginField{siteLabel}
\fieldDeclaration{private JLabel siteLabel}
\closeField

\beginField{siteTextField}
\fieldDeclaration{private JTextFiels siteTextField}
\closeField

\beginField{commentLabel}
\fieldDeclaration{private JLabel commentLabel}
\closeField

\beginField{commentTextField}
\fieldDeclaration{private JTextFiels commentTextField}
\closeField

\beginField{latitudeLabel}
\fieldDeclaration{private JLabel latitudeLabel}
\closeField

\beginField{latitudeTextField}
\fieldDeclaration{private JTextFiels latitudeTextField}
\closeField

\beginField{longLabel}
\fieldDeclaration{private JLabel longLabel}
\closeField

\beginField{longTextField}
\fieldDeclaration{private JTextFiels longTextField}
\closeField

\beginField{strikeLabel}
\fieldDeclaration{private JLabel strikeLabel}
\closeField

\beginField{strikeTextField}
\fieldDeclaration{private JTextFiels strikeTextField}
\closeField

\beginField{dipLabel}
\fieldDeclaration{private JLabel dipLabel}
\closeField

\beginField{dipTextField}
\fieldDeclaration{private JTextFiels dipTextField}
\closeField

\beginField{volumeLabel}
\fieldDeclaration{private JLabel volumeLabel}
\closeField

\beginField{volumeTextField}
\fieldDeclaration{private JTextFiels volumeTextField}
\closeField

\beginField{massLabel}
\fieldDeclaration{private JLabel massLabel}
\closeField

\beginField{massTextField}
\fieldDeclaration{private JTextFiels massTextField}
\closeField

\beginField{sampleType}
\fieldDeclaration{private ButtonGroup sampleType}
\fieldComment{Groups coreSample and handSample radiobuttons.}
\closeField

\beginField{coreSample}
\fieldDeclaration{private JRadioButton coreSample}
\closeField

\beginField{handSample}
\fieldDeclaration{private JRadioButton handSample}
\closeField

\beginMethod{ProjectInformationPanel()}
\methodDeclaration{public ProjectInformationPanel()}
\methodComment{Creates default ProjectInformationPanel.}
\closeMethod

\beginMethod{ProjectInformationPanel(Project)}
\methodDeclaration{public ProjectInformationPanel(Project project)}
\methodComment{Creates ProjectInformationPanel with information taken from project.}
\closeMethod

\beginMethod{setProject(Project)}
\methodDeclaration{private void setProject(Project project)}
\methodComment{Calls super.setProject(project) and updates textfield
with new projects data.}
\closeMethod
