\beginClass{ProjectComponent}
\classComment{
	Generic gui component which uses Project and listens MeasurementEvents and ProjectEvents.
}
\classPackage{ikayaki.gui}
\classDeclaration{public class ProjectComponent}
\classExtends{JPanel}
\classCreatedBy{MainViewPanel}
\classUses{Project}
\classSubclass{ProjectInformationPanel}
\classSubclass{MeasurementSequencePanel}
\classSubclass{MeasurementDetailsPanel}
\classSubclass{MeasurementControlsPanel}
\classSubclass{MeasurementGraphsPanel}
\classSubclass{ProjectExplorerPanel}
\classSubclass{CalibrationPanel}
\classEvent{On ProjectEvent}{does nothing; subclasses may override this.}
\classEvent{On MeasurementEvent}{does nothing; subclasses may override this.}
\closeClass

\beginField{project}
\fieldDeclaration{private Project project}
\fieldComment{The active project.}
\closeField

\beginMethod{ProjectComponent()}
\methodDeclaration{public ProjectComponent()}
\methodComment{Initializes this ProjectComponent with no project (one probably arrives shortly with setProject(Project)).}
\closeMethod

\beginMethod{getProject()}
\methodDeclaration{public Project getProject()}
\methodReturn{the active project, or null if no project is active.}
\closeMethod

\beginMethod{setProject(Project)}
\methodDeclaration{public void setProject(Project project)}
\methodComment{
	Sets the project for this ProjectComponent. Unregisters MeasurementListener and ProjectListener from the old project, and registers them to the new project.
}
\methodParam{project}{new active project, or null to make no project active.}
\closeMethod

\beginMethod{projectUpdated(ProjectEvent)}
\methodDeclaration{public void projectUpdated(ProjectEvent event)}
\methodComment{
	Does nothing; subclasses override this if they want to listen ProjectEvents.
}
\methodParam{event}{ProjectEvent received.}
\closeMethod

\beginMethod{measurementUpdated(MeasurementEvent)}
\methodDeclaration{public void measurementUpdated(MeasurementEvent event)}
\methodComment{
	Does nothing; subclasses override this if they want to listen MeasurementEvents.
}
\methodParam{event}{MeasurementEvent received.}
\closeMethod
