\beginClass{MeasurementControlsPanel}
\classComment{
	Has "Measure"/"Pause", "Single step" and "Stop now!" buttons for controlling measurements; "+z/-z" radiobuttons for changing sample orientation used in calculations, help picture for inserting sample, picture of current magnetometer status, and, manual controls.

	Listens MeasurementEvents and ProjectEvents, and updates buttons and magnetometer status accordingly.
}
\classPackage{ikayaki.gui}
\classDeclaration{public class MeasurementControlsPanel}
\classExtends{ProjectComponent}
\classCreatedBy{MainViewPanel}
\classUses{Project}
\classUses{MagnetometerStatusPanel}
\classUses{ManualControlsPanel}
\classEvent{On measureButton click}{call project.doAutoStep() or project.doPause(), depending on current button status. Show error message if false is returned.}
\classEvent{On singlestepButton click}{call project.doSingleStep(); show error message if false is returned.}
\classEvent{On stopButton click}{call project.doAbort(); show critical error message if false is returned.}
\classEvent{On z{Plus,Minus}RadioButton click}{call project.setOrientation(boolean) where Plus is true and Minus is false.}
\classEvent{On ProjectEvent}{update buttons and manual controls according to project.isXXXEnabled().}
\classEvent{On MeasurementEvent}{call magnetometerStatusPanel.updateStatus(int, int) with the right values from MeasurementEvent.}
\closeClass

\beginField{measureButton}
\fieldDeclaration{private JButton measureButton}
\fieldComment{Measure/pause -button; "Measure" when no measuring is being done, "Pause" when there is ongoing measuring sequence.}
\closeField

\beginField{singlestepButton}
\fieldDeclaration{private JButton singlestepButton}
\closeField

\beginField{stopButton}
\fieldDeclaration{private JButton stopButton}
\closeField

\beginField{zButtonGroup}
\fieldDeclaration{private ButtonGroup zButtonGroup}
\fieldComment{Groups together +z and -z RadioButtons.}
\closeField

\beginField{zPlusRadioButton}
\fieldDeclaration{private JRadioButton zPlusRadioButton}
\fieldComment{Changes sample orientation to +Z.}
\closeField

\beginField{zMinusRadioButton}
\fieldDeclaration{private JRadioButton zMinusRadioButton}
\fieldComment{Changes sample orientation to -Z.}
\closeField

\beginField{sampleInsertPanel}
\fieldDeclaration{private JPanel sampleInsertPanel}
\fieldComment{Draws a help image and text for sample inserting: "Put sample in holder arrow up."}
\closeField

\beginField{magnetometerStatusPanel}
\fieldDeclaration{private MagnetometerStatusPanel magnetometerStatusPanel}
\closeField

\beginField{manualControlsPanel}
\fieldDeclaration{private ManualControlsPanel manualControlsPanel}
\closeField


\beginClass{MagnetometerStatusPanel}
\classComment{Picture of current magnetometer status, with sample holder position and rotation. Status is updated according to MeasurementEvents received by MeasurementControlsPanel.}
\classPackage{ikayaki.gui}
\classDeclaration{public class MagnetometerStatusPanel}
\classExtends{JPanel}
\classCreatedBy{MeasurementControlsPanel}
\closeClass

\beginToc
\tocMethod{MagnetometerStatusPanel()}
\tocMethod{updateStatus(int,int)}
\closeToc

\beginMethod{MagnetometerStatusPanel()}
\methodDeclaration{public MagnetometerStatusPanel()}
\methodComment{Sets magnetometer status to current position.}
\closeMethod

\beginMethod{updateStatus(int,int)}
\methodDeclaration{public void updateStatus(int position, int rotation)}
\methodComment{Updates magnetometer status picture; called by MeasurementControlsPanel when it receives MeasurementEvent.}
\methodParam{position}{sample holder position, from 1 to 16777215.}
\methodParam{rotation}{sample holder rotation, from 0 (angle 0) to 2000 (angle 360).}
\closeMethod


\beginClass{ManualControlsPanel}
\classComment{Magnetometer manual controls. MeasurementControlsPanel disables these whenever a normal measurement step is going.}
\classPackage{ikayaki.gui}
\classDeclaration{public class ManualControlsPanel}
\classExtends{JPanel}
\classCreatedBy{MeasurementControlsPanel}
\classUses{Project}
\classUses{Settings}
\classEvent{On moveXXX click}{call project.doManualMove(int) with clicked position. If false is returned, show small error message. Position values are found from Settings; demagZ is Settings.instance().getAxialAFPosition() and demagY is Settings.instance().getTransverseYAFPosition().}
\classEvent{On rotateXXX click}{call project.doManualRotate(int) with clicked angle. If false is returned, show small error message.}
\classEvent{On measureAllButton click}{call project.doManualMeasure(). If false is returned, show small error message.}
\classEvent{On resetAllButton click}{call project.doManualReset()? If false is returned, show small error message.}
\classEvent{On DemagZButton click}{call project.doManualDemagZ(double) with value from demagAmplitudeField. If false is returned, show small error message.}
\classEvent{On DemagYButton click}{call project.doManualDemagY(double) with value from demagAmplitudeField. If false is returned, show small error message.}
\closeClass

\beginField{moveButtonGroup}
\fieldDeclaration{private ButtonGroup moveButtonGroup}
\fieldComment{Groups together all sample holder moving RadioButtons (moveXXX).}
\closeField

\beginField{moveHome}
\fieldDeclaration{private JRadioButton moveHome}
\fieldComment{Moves sample holder to home position.}
\closeField

\beginField{moveDemagZ}
\fieldDeclaration{private JRadioButton moveDemagZ}
\fieldComment{Moves sample holder to demagnetize-Z position.}
\closeField

\beginField{moveDemagY}
\fieldDeclaration{private JRadioButton moveDemagY}
\fieldComment{Moves sample holder to demagnetize-Y position.}
\closeField

\beginField{moveBG}
\fieldDeclaration{private JRadioButton moveBG}
\fieldComment{Moves sample holder to background position.}
\closeField

\beginField{moveMeasure}
\fieldDeclaration{private JRadioButton moveMeasure}
\fieldComment{Moves sample holder to measurement position.}
\closeField

\beginField{rotateButtonGroup}
\fieldDeclaration{private ButtonGroup rotateButtonGroup}
\fieldComment{Groups together all sample holder rotating RadioButtons (rotateXXX).}
\closeField

\beginField{rotate0}
\fieldDeclaration{private JRadioButton rotate0}
\fieldComment{Rotates sample holder to angle 0.}
\closeField

\beginField{rotate90}
\fieldDeclaration{private JRadioButton rotate90}
\fieldComment{Rotates sample holder to angle 90.}
\closeField

\beginField{rotate180}
\fieldDeclaration{private JRadioButton rotate180}
\fieldComment{Rotates sample holder to angle 180.}
\closeField

\beginField{rotate270}
\fieldDeclaration{private JRadioButton rotate270}
\fieldComment{Rotates sample holder to angle 270.}
\closeField

\beginField{measureAllButton}
\fieldDeclaration{private JButton measureAllButton}
\fieldComment{Measures X, Y and Z (at current sample holder position) by calling project.doManualMeasure().}
\closeField

\beginField{resetAllButton}
\fieldDeclaration{private JButton resetAllButton}
\fieldComment{Resets X, Y and Z by calling project.doManualReset()? Does what?}
\closeField

\beginField{demagAmplitudeField}
\fieldDeclaration{private JTextField demagAmplitudeField}
\fieldComment{Demagnetization amplitude in mT, used when demag{Z,Y}Button is clicked.}
\closeField

\beginField{demagZButton}
\fieldDeclaration{private JButton demagZButton}
\fieldComment{Demagnetizes in Z (at current sample holder position) by calling project.doManualDemagZ(double).}
\closeField

\beginField{demagYButton}
\fieldDeclaration{private JButton demagYButton}
\fieldComment{Demagnetizes in Y (at current sample holder position) by calling project.doManualDemagY(double).}
\closeField
