\beginClass{SettingsPanel}
\classComment{Creates its components and updats changes to Settings and saves them in Configuration file}
\classPackage{ikayaki.gui}
\classDeclaration{public class SettingsPanel}
\classExtends{JFrame}
\classCreatedBy{MainStatusBar}
\classUses{Settings}
\classUses{Squid}
\classEvent{On Save Clicked}{saves current configuration to Settings-singleton and closes window}
\classEvent{On Cancel Clicked}{closes window (discarding changes)}
\closeClass

\beginField{magnetometerPort}
\fieldDeclaration{private JComboBox magnetometerPort}
\fieldComment{COM port for magnetometer}
\closeField

\beginField{demagnetizerPort}
\fieldDeclaration{private JComboBox demagnetizerPort}
\fieldComment{COM port for demagnetizer, can be sharing same port with magnetometer}
\closeField

\beginField{handlerPort}
\fieldDeclaration{private JComboBox handlerPort}
\fieldComment{COM port for sample handler}
\closeField

\beginField{xAxisCalibration}
\fieldDeclaration{private JTextField xAxisCalibration}
\fieldComment{Calibration constants with polarization (factory set?)}
\closeField

\beginField{yAxisCalibration}
\fieldDeclaration{private JTextField yAxisCalibration}
\fieldComment{Calibration constants with polarization (factory set?)}
\closeField

\beginField{zAxisCalibration}
\fieldDeclaration{private JTextField zAxisCalibration}
\fieldComment{Calibration constants with polarization (factory set?)}
\closeField

\beginField{demagRamp}
\fieldDeclaration{private JComboBox demagRamp}
\fieldComment{how fast demagnetization goes}
\closeField

\beginField{demagDelay}
\fieldDeclaration{private JComboBox demagDelay}
\fieldComment{?}
\closeField

\beginField{acceleration}
\fieldDeclaration{private JTextField acceleration}
\fieldComment{Handler acceleration}
\closeField

\beginField{deceleration}
\fieldDeclaration{private JTextField deceleration}
\fieldComment{Handler deceleration}
\closeField

\beginField{velocity}
\fieldDeclaration{private JTextField velocity}
\fieldComment{Handler Max speed}
\closeField

\beginField{measurementVelocity}
\fieldDeclaration{private JTextField measurementVelocity}
\fieldComment{speed in measurement, should be small}
\closeField

\beginField{transverseYAFPosition}
\fieldDeclaration{private JTextField transverseYAFPosition}
\fieldComment{AF demag position for transverse}
\closeField

\beginField{axialAFPosition}
\fieldDeclaration{private JTextField axialAFPosition}
\fieldComment{axial AF demag position in steps, must be divisible by 10. Relative to Home.}
\closeField

\beginField{sampleLoadPosition}
\fieldDeclaration{private JTextField sampleLoadPosition}
\fieldComment{Position in steps, must be divisible by 10. Relative to Home. (same as Home?)}
\closeField

\beginField{backgroundPosition}
\fieldDeclaration{private JTextField backgroundPosition}
\fieldComment{Position in steps, must be divisible by 10. Relative to Home.}
\closeField

\beginField{measurementPosition}
\fieldDeclaration{private JTextField measurementPosition}
\fieldComment{Position in steps, must be divisible by 10. Relative to Home.}
\closeField

\beginField{rotation}
\fieldDeclaration{private JTextField rotation}
\fieldComment{steps to perform full rotation, must be clockwise, determined by sign}
\closeField

\beginField{handlerRightLimit}
\fieldDeclaration{private JComboBox handlerRightLimit}
\fieldComment{Refers to right limit switch on translation axis. And usually sample holder motion toward right limit is posivitive direction (default).}
\closeField

\beginField{saveButton}
\fieldDeclaration{private JButton saveButton}
\closeField

\beginField{cancelButton}
\fieldDeclaration{private JButton cancelButton}
\closeField


\beginMethod{SettingsPanel()}
\methodDeclaration{public SettingsPanel()}
\methodComment{
    Creates all components and puts them in right places. Labels are created only here (no global fields). Creates ActionListeners for buttons.
}
\closeMethod

\beginMethod{closeWindow()}
\methodDeclaration{public void closeWindow()}
\methodComment{
    Closes window, no changes saved.
}
\closeMethod

\beginMethod{saveSettings()}
\methodDeclaration{public void saveSettings()}
\methodComment{
    Saves all settings to Settings-singleton and calls closeWindow().
}
\closeMethod
